Supplementary Information: \nTree height, microhabitat, and hydraulic traits shape drought responses in a temperate broadleaf forest

### 2020-07-12 manuscript/climate_sensitivity_SI.Rmd
update row packing in table S5
#99

\newpage
```{r table S5, eval = TRUE, echo=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
multivar_table <- read.csv("tables_figures/publication/tableS5_multivariable_models_reform_arimaratio.csv", stringsAsFactors = FALSE, check.names = FALSE) 
kable(multivar_table, booktabs = TRUE, caption = "Table S5. Summary of top full models for each drought instance, where $Rt_{ARIMA}$ is used as the response variable. ", format = 'latex', escape = FALSE) %>%
  kable_styling(latex_options = c("scale_down", "hold_position"), font_size = 12, protect_latex = TRUE) %>%
  add_header_above(c(" "," "," "," "," ", " ", " ", "crown position" = 4, 
                     " "," ")) %>%
  pack_rows("", 1, 1, latex_gap_space = ".4em", colnum = 1, hline_before = FALSE) %>%
  pack_rows("", 2, 2, latex_gap_space = ".4em", colnum = 1, hline_before = FALSE) %>%
  pack_rows("", 3, 4, latex_gap_space = ".4em", colnum = 1, hline_before = FALSE) %>%
  pack_rows("", 5, 5, latex_gap_space = ".4em", colnum = 1, hline_before = FALSE) %>%
  row_spec(1, bold = T) %>%
  row_spec(2, bold = T) %>%
  row_spec(3, bold = T) %>%
  row_spec(5, bold = T) %>%
  kable_styling()
```
Models are ranked by AICc. Shown are all models whose AICc value falls within 1.0 ($\Delta$AICc<1) of the best model (bold).

>>>>

\newpage
```{r table S5, eval = TRUE, echo=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
multivar_table <- read.csv("tables_figures/publication/tableS5_multivariable_models_reform_arimaratio.csv", stringsAsFactors = FALSE, check.names = FALSE) 
kable(multivar_table, booktabs = TRUE, caption = "Table S5. Summary of top full models for each drought instance, where $Rt_{ARIMA}$ is used as the response variable. ", format = 'latex', escape = FALSE) %>%
  kable_styling(latex_options = c("scale_down", "hold_position"), font_size = 12, protect_latex = TRUE) %>%
  add_header_above(c(" "," "," "," "," ", " ", " ", "crown position" = 4, 
                     " "," ")) %>%
  pack_rows("", 1, 2, latex_gap_space = ".4em", colnum = 1, hline_before = FALSE) %>%
  pack_rows("", 3, 4, latex_gap_space = ".4em", colnum = 1, hline_before = FALSE) %>%
  pack_rows("", 5, 8, latex_gap_space = ".4em", colnum = 1, hline_before = FALSE) %>%
  pack_rows("", 9, 11, latex_gap_space = ".4em", colnum = 1, hline_before = FALSE) %>%
  row_spec(1, bold = T) %>%
  row_spec(3, bold = T) %>%
  row_spec(5, bold = T) %>%
  row_spec(9, bold = T) %>%
  kable_styling()
```
Models are ranked by AICc. Shown are all models whose AICc value falls within 1.0 ($\Delta$AICc<1) of the best model (bold).
